In the grand scheme of things, \textit{Cloud Computing} is still a relative new development which
has seen rapid growth in recent years and with that has seen a lot of technologies emerge around it.
One of those is the concept of \textit{Serverless Computing} or \textit{Function as a Service
(FaaS)}. Due to its versatile nature, a lot of big players in the cloud computing field jumped on it
and have their own implementation in their portfolio.

\\

Likewise, the \textit{Internet of Things (IoT)} has also seen large adoption in many aspects of life
and is an integral part of it. Be it for household appliances or in industrial applications,
\textit{IoT} devices can be found everywhere.

\\

This bachelor thesis tries to show the usefulness of \textit{Serverless Computing} in conjunction
with \textit{IoT} devices by building an infrastructure to host \textit{serverless functions} where
all \textit{IoT} devices can then send their data to. While not a classic \textit{IoT} device, there
is also support for both \textit{Android} and \textit{iOS} devices to transmit data. This data is
then further used for analytics and visualised with graphs in a web interface. In order to achieve
this we decided to use the \textit{OpenFaaS} framework to realise the hosting function platform.
Furthermore, \textit{Kafka} is used to manage all incoming requests from devices. \textit{Kafka}
also handles the forwarding of requests to functions. For persistence of sensor data we are using
the \textit{NoSQL} database \textit{MongoDB}. The database is of great help when confronted with
data of \textit{IoT} devices. Having a stack like this also means dealing with a lot of
configuration. To aid this process, we also developed a \textit{Rake} script which makes everything
runnable with only one command. And finally, we are using \textit{Azure Pipelines} as our
verification tool to test all parts of our stack and push our \textit{serverless functions} to an
online registry, which makes deployment even faster.

\\

In the final chapter of this thesis, we present results including benchmarks for running our stack
on affordable hardware, showing just how cost-effective and yet powerful a serverless stack can be.
