\subsection{MongoDB}

While our technology stack for the most part was nice to work with, we still had our fair share of
problems. One of the most significant one was in relation to our \textit{MongoDB} database.
\textit{MongoDB’s API design} is confusing to say the least. Questionable deprecation choices and
multiple connect interfaces are the most rampant examples. Once we got past those issues and got a
grasp how it all works, \textit{MongoDB} does seem to be a decent choice for our task at hand.
Mainly because of its JSON-like document architecture. Posting the same \textit{JSON} uniformly from
all devices to the \textit{Kafka RESt endpoint} is a fairly trivial task. The architecture of our
\textit{sensordata} database is as follows: every sensor type has its own document with the device
id of the sender, the time stamp when the sensor data was collected and a unique id per entry. The
document is then named after the sensor type itself. Those documents differ depending on whether the
sensor only emits one value or multiple values. An example for a single value sensor document would
be \textit{pressure} and an example with multiple values would be \textit{orientation}, where the
sensor collects its orientation value of the x,y and z axis. We also need one document for all the
devices that are registered, called \textit{devices} with a unique id per entry, the name of the
device and the supported sensor or data types. Devices have to be registered in order for the
\textit{UI} to know which graphs it has to display for every device.

\begin{code}[H]
  \centering
  \begin{lstlisting}[basicstyle=\small\ttfamily]
    {
      _id: 'c7704c421d7491ec',
      name: 'Samsung Galaxy S7',
      data_types: [
          'cpu_frequency',
          'proximity',
          'acceleration',
          'rotation',
          'pressure',
          'orientation',
          'gravity',
          'illuminance',
          'rotation_rate',
          'rotation_rate_uncalibrated',
          'magnetic_field',
          'magnetic_field_uncalibrated'
      ]
    }
  \end{lstlisting}
  \caption{Registered device “Samsung Galaxy S7” with all its supported data and sensor types.}
\end{code}
